---
title: "HW8"
author: "Dillon, Eliott, Simone"
date: "11/15/2021"
output: pdf_document
bibliography: bib.bib
nocite: '@*'
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 6.5, fig.height = 8)
library(here)
library(rio)
library(tidyverse)
library(janitor)

star <- import(here("Data", "star.csv")) %>% clean_names()


```

```{r}
View(star)
```

```{r commit 3}
star %>% 
  group_by(sex, frl) %>% 
  summarize(math_mean = mean(tmathss, na.rm = TRUE),
            math_sd = sd(tmathss, na.rm = TRUE),
            rdg_mean = mean(treadss, na.rm = TRUE), 
            rdg_sd = sd(treadss, na.rm = TRUE))

```
The table shows the mean math and reading scores separated by sex and frl (?), as well as the standard deviations for these scores.

Two of my favorite citation examples in different formats are @hammitt_admissible_2013 and of course [@barsky_preference_1997]. Bangers.

\newpage
**REFERENCES**

### Commit 4 Graph Description

The graph shows that the more experienced a teacher is in terms of number of years of teaching, the higher level of math scores students will achieve regardless of whether they are receiving a free/reduced lunch or a paid meal, compared to students under less experienced teachers. In this sense, we can interpret lunch type as a proxy for socioeconomic status (i.e. free/reduced = low income; paid = middle - to high income). While the level of teacher experience doesn't minimize the achievement gap in math scores between students receiving a free/reduced lunch vs. paid, it appears that teacher experience has a positive net impact on both groups. In other words, to improve math scores globally, teacher experience is key. However, to reduce math score inequity, additional interventions may be needed. 

```{r commit 4}


star$frl <- factor(star$frl, levels = c("yes", "no"))


plot<- star %>% 
  ggplot(aes(totexp, tmathss)) +
  geom_point(color = "gray", size = 1.5) +
 geom_smooth(aes(group = frl, color = frl), method="lm", size=1.25) +
  theme_minimal() +
  labs(title = "Relation between teacher experience and math scores",
       subtitle = "Separate regression lines displayed by free/reduced price lunch status",
       x = "Teacher Experience (years)",
       y = "Total Math Scale Scores",
       color = "Lunch Status")

plot + theme(legend.position = "bottom") +
  scale_fill_discrete(name = "Lunch Status") +
  scale_color_hue(labels = c("Free/Reduced Price Meals", "Paid Meals"))

```

